\vspace {5mm}
\centerline
{\zihao{5}
\begin{CJK*}{GBK}{hei}²Î~¿¼~ÎÄ~Ï×\end{CJK*}}

\begin{thebibliography}{99}
\bibliography{ref.bib}
\zihao{5-} \addtolength{\itemsep}{-1em}
\vspace {1.5mm}

\bibitem[1]{1} Rui C, Qingyi H, Yan-Shuo C, et al. A survey of collaborative filtering-Based recommender systems: from traditional methods to hybrid methods based on social networks. IEEE Access, 2018, 6: 64301-64320

\bibitem[2]{2} Sarwar B, Karypis G, Konstan J, Riedl J. Item-based Collaborative Filtering Recommendation Algorithms. Proceedings of the 10th international conference on World Wide Web. ACM, New York, pp 285?C295
\bibitem[3]{3} Belkin N.J., Croft W.B.  Information filtering and information retrieval: two sides of the same coin? Commun ACM 35(12):29?C38
\bibitem[4]{4} Wu HC, Luk RWP, Wong KF, Kwok KL Interpreting tf-idf term weights as making relevance decisions. ACM Trans Inf Syst (TOIS) 26(3):13
\bibitem[5]{5} Adomavicius G, Tuzhilin A. Toward the next generation of recommender systems: a survey of the state-of-the-art and possible extensions. IEEE Trans Knowl Data Eng 17(6):734?C749
\bibitem[6]{6} Su X, Khoshgoftaar T. A survey of collaborative filtering techniques. Adv Artif Intell 2009:4
\bibitem[7]{7}Tang J, Hu X, Gao H, Liu H. Exploiting local and global social context for recommendation
\bibitem[8]{8}Claypool M, Gokhale A, Mir T, Mir T, Murnikov P, Netes D, Sartin M. Combining content-based and collaborative filters in a online newspaper. In: Proc. of the ACM SIGIR Workshop on Recommender Systems. 1999.
\bibitem[9]{9}Hu YF, Koren Y, Volinsky C. Collaborative Filtering for Implicit Feedback Datasets. IEEE International Conference on Data Mining 2008: 263-+
\bibitem[10]{10}Good N, Schafer JB, Konstan JA, Borchers A, Sarwar B, Herlocker J, Riedl J. Combining collaborative filtering with personal agents for better recommendations. In: Proceedings of the national conference on artificial intelligence, pp 439?C446
\bibitem[11]{11}Soboroff I, Nicholas . Combining content and collaboration in text filtering. Proceedings of international joint conference on artificial intelligence workshop: machine learning for information filtering

\bibitem[12]{12} Marsden, P. V., and Friedkin, N. E. Network studies of social influence. Sociological Methods \& Research. 1993, 22(1):127-151

\bibitem[13]{13} Mcpherson, M., Smithlovin, L., and Cook, J. M. Birds of a feather: Homophily in social networks. Annual Review of Sociology. 2001, 27(1):415?C444

\bibitem[14]{14} Tang J, Hu X, Liu H. Social recommendation: a review. Social Network Analysis and Mining. 2013, 3(4): 1113-1133

\bibitem[15]{15} Liu Y, Yang C, Ma J, et al. A social recommendation system for academic collaboration in undergraduate research. Expert Systems. 2019, 36(2): e12365

\bibitem[16]{16} Golbeck J. Generating Predictive Movie Recommendations from Trust in Social Networks. Trust Management. Berlin, Heidelberg, Springer, 2006: 93-104

\bibitem[17]{17} Golbeck, J. Personalizing applications through integration of inferred trust values in semantic web-based social networks. Proceedings of Semantic Network Analysis Workshop, Galway, Ireland, 2005

\bibitem[18]{18} Massa P, Avesani P. Trust metrics on controversial users: Balancing between tyranny of the majority and echo chambers. International Journal on Semantic Web and Information Systems - IJSWIS. 2007, 3

\bibitem[19]{19} Massa P, Avesani P. Trust-aware recommender systems. Proceedings of the 2007 ACM conference on Recommender systems, Minneapolis, MN, USA, 2007: 17-24

\bibitem[20]{20} Moradi P, Ahmadian S. A reliability-based recommendation method to improve trust-aware recommender systems. Expert Systems with Applications. 2015, 42(21): 7386-7398



\bibitem[21]{21} Kipf T N, Welling M. Semi-supervised classification with graph convolutional networks[J]. arXiv preprint arXiv:1609.02907, 2016.
\bibitem[22]{22} Hamilton W L, Ying R, Leskovec J. Inductive representation learning on large graphs[J]. arXiv preprint arXiv:1706.02216, 2017.

\bibitem[23]{23} Xu K, Li C, Tian Y, et al. Representation learning on graphs with jumping knowledge networks[C]. PMLR, 2018: 5453-5462.
\bibitem[24]{24} Chen J, Ma T, Xiao C. Fastgcn: fast learning with graph convolutional networks via importance sampling[J]. arXiv preprint arXiv:1801.10247, 2018.
\bibitem[25]{25} Chiang W L, Liu X, Si S, et al. Cluster-gcn: An efficient algorithm for training deep and large graph convolutional networks[C]. 2019: 257-266.
\bibitem[26]{26} Zeng H, Zhou H, Srivastava A, et al. Graphsaint: Graph sampling based inductive learning method[J]. arXiv preprint arXiv:1907.04931, 2019.
\bibitem[27]{27} Li Y, Tarlow D, Brockschmidt M, et al. Gated graph sequence neural networks[J]. arXiv preprint arXiv:1511.05493, 2015.
\bibitem[28]{28} Veli?kovi? P, Cucurull G, Casanova A, et al. Graph attention networks[J]. arXiv preprint arXiv:1710.10903, 2017.

\bibitem[29]{beamer2012direction} Scott Beamer, Krste Asanovic, and David Patterson. Direction-optimizing breadth-first search. In SC¡¯12: Proceedings of the International Conference on High Performance Computing, Networking, Storage and Analysis, pages 1¨C10. IEEE, 2012.

\bibitem[30]{fan2018deep} Wenqi Fan, Qing Li, and Min Cheng. Deep modeling of social relations for recommendation. In Proceedings of the AAAI Conference on Artificial Intelligence, volume 32, 2018.

\bibitem[31]{fan2019graph} Wenqi Fan, Yao Ma, Qing Li, Yuan He, Eric Zhao, Jiliang Tang, and Dawei Yin. Graph neural networks for social recommendation. In The World Wide Web Conference, pages 417¨C426, 2019.

\bibitem[32]{fan2019deep} Wenqi Fan, Yao Ma, Dawei Yin, Jianping Wang, Jiliang Tang, and Qing Li. Deep social collaborative filtering. In Proceedings of the 13th ACM Conference on Recommender Systems, pages 305¨C313, 2019.

\bibitem[33]{Goldberg2014word2vecED} Y. Goldberg and Omer Levy. word2vec explained: deriving mikolov et al.¡¯s negative-sampling word-embedding method. ArXiv, abs/1402.3722, 2014.

\bibitem[34]{grover2016node2vec} Aditya Grover and Jure Leskovec. node2vec: Scalable feature learning for networks. In Proceedings of the 22nd ACM SIGKDD international conference on Knowledge discovery and data mining, pages 855¨C864, 2016.

\bibitem[35]{lu2011link} Linyuan Lu and Tao Zhou. Link prediction in complex networks: A survey. Physica A: statistical mechanics and its applications, 390(6):1150¨C1170, 2011.

\bibitem[36]{Ma2008SoRecSR} Hao Ma, Haixuan Yang, Michael R. Lyu, and Irwin King. Sorec: social recommendation using probabilistic matrix factorization. In CIKM ¡¯08, 2008.


\bibitem[37]{mikolov2013efficient} Tomas Mikolov, Kai Chen, Greg Corrado, and Jeffrey Dean. Efficient estimation of word representations in vector space. arXiv preprint arXiv:1301.3781, 2013.

\bibitem[38]{Perozzi2014DeepWalkOL}  Bryan Perozzi, Rami Al-Rfou, and S. Skiena. Deepwalk: online learning of social representations. Proceedings of the 20th ACM SIGKDD international conference on Knowledge discovery and data mining, 2014.

\bibitem[39]{van2014renyi} Jurgen Schmidhuber. Deep learning in neural networks: An overview. Neural networks, 61:85¨C117, 2015.

\bibitem[40]{tang2015line} Jian Tang, Meng Qu, Mingzhe Wang, Ming Zhang, Jun Yan, and Qiaozhu Mei. Line: Large-scale information network embedding. In Proceedings of the 24th international conference on world wide web, pages 1067¨C1077, 2015.

\bibitem[41]{tarjan1972depth} Robert Tarjan. Depth-first search and linear graph algorithms. SIAM journal on computing, 1(2):146¨C160, 1972.

\bibitem[42]{van2014renyi} Tim Van Erven and Peter Harremos. Renyi divergence and kullback-leibler divergence. IEEE Transactions on Information Theory, 60(7):3797¨C3820, 2014.

\bibitem[43]{wang2016structural} Daixin Wang, Peng Cui, and Wenwu Zhu. Structural deep network embedding. In Proceedings of the 22nd ACM SIGKDD international conference on Knowledge discovery and data mining, pages 1225¨C1234, 2016.
% \bibitem[1]{1}
% ?????????(??????The Cooperative
% Association for Internet Data Analysis(CAIDA),http://www.caida.org/data
% 2010,7,18) \textbf{*?????????????????????????????1????????*}\footnote{The Cooperative Association for Internet Data
% Analysis (CAIDA), http://www.caida.org/data 2010, 7, 18}

% \bibitem[2]{2} ?????¦Ï????????????????????????[3]??

% \bibitem[3]{3} Zhou Yong-Bin, Feng Deng-Guo. Design and analysis of cryptographic
% protocols for RFID. Chinese Journal of Computers, 2006, 29(4): 581-589 (in
% Chinese) \newline
% (??????, ????. RFID???§¿???????????. ????????, 2006, 29(4): 581-589)

% \bibitem[4]{4} ????????î”?üž???????????§Õ??

% \bibitem[5]{5} ????(????????????????????§Õ, ???).
% ???(??????????????§Õ????????§³§Õ)????????(?????). ????(???), ??,
% ??(??): ??? \textbf{*?????????*}

% \bibitem[6]{6}????.
% ???????(????????1?????§Õ????????§³§Õ)????????(?????)//Proceedings of
% the {\ldots} (????????). ???????????, ??????????????????, ??: ???
% \textbf{*???????????????*}

% \bibitem[7]{7}????. ???????(??????????????§Õ, ??????§³§Õ):
% ??????(?????)//????. ???????. ?????: ??????, ??????: ???
% \textbf{*??????*}

% \bibitem[8]{8}????. ????: ??????(?????). ???(???ÖÎ§Õ). ????????: ??????,
% ?????? \textbf{*?üž???*}

% \bibitem[9]{9}????. ???????[????¦Ë????/???¦Ë????]. ??¦Ë????,??¦Ë???, ??
% \textbf{*?¦Ë??????*}

% \bibitem[10]{10}????. ???????(??????????????§Õ????????§³§Õ). ??¦Ë???: ??¦Ë,
% ????????: ??????, ?? \textbf{*????????*}

% \bibitem[11]{11}????????. ?????????????????????????????
% \textbf{*???????*}
\end{thebibliography}

